In the following sections, we will present the results of our experiments and
evaluate how Multipath TCP performs on a host with multiple wireless
interfaces available to it.

\S\ref{sec:results-interference} examines the effect of wireless
interference on simultaneous clients irrespective of Multipath TCP.\@ This is
done to determine to what extent this will affect the quality of the individual
wireless links.

\S\ref{sec:results-mptcp} presents the results of running a Multipath TCP
connection over wireless without Coupled congestion control. The purpose of this
is to show whether an MPTCP client with both wireless networks to itself can
ever reach the same throughput as two TCP flows running on two hosts on
the different networks.

\S\ref{sec:results-fairness} evaluates the extent to which Multipath TCP behaves
fairly when competing with other flows on the wireless networks. For the uplink
case we give an analysis of how and why Multipath TCP exhibits unfair behaviour.

\S\ref{sec:results-performance} examines the performance of Coupled Multipath 
TCP on idle paths. This is done in order to determine the how well it would 
utilize the links in this scenario.

In \S\ref{sec:results-reacting} we present results showing how Multipath TCP 
reacts to changes in a mobile environment.

Finally, \S\ref{sec:results-closing-remarks} explains several strange phenomenon
we observed during our wireless experiments, as well as give some closing
thought about our experiments.
% vim:textwidth=80:colorcolumn=80:spell:
